%-------------------------
% Resume in Latex
% Author : Devi Eswar Kumar Damerla
% Optimized for ATS
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}} 

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Devi Eswar Kumar Damerla} \\ \vspace{1pt}
    \small \href{mailto:devieswar79@gmail.com}{\underline{devieswar79@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/devi-eswar-kumar-damerla}{\underline{linkedin.com/in/devi-eswar-kumar-damerla}} $|$
    \href{https://devieswar.github.io/}{\underline{devieswar.github.io}} 
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
\small{
Full-Stack Software Engineer with 5+ years of experience delivering scalable, production-grade systems across web, cloud, and AI/ML domains. Expert in full-stack development leveraging FastAPI, Node.js, NestJS, Angular, and React with proven capability to architect and deploy end-to-end applications. Specialized in embedding AI/ML solutions including Large Language Models (LLMs), Retrieval-Augmented Generation (RAG), and knowledge graph architectures into production environments. Proficient in cloud infrastructure (AWS SageMaker, Bedrock, ECS Fargate), microservices architecture, and DevOps methodologies (Docker, Kubernetes, CI/CD). Demonstrated track record of generating measurable business impact through technical innovation and cross-functional collaboration.
}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Engineer}{Nov 2024 -- Present}
      {AI for ALL LLC (AI OWL)}{Columbus, OH}
      \resumeItemListStart
        \resumeItem{Lead engineer for Flash AI, a CJIS-compliant evidence intelligence platform enabling secure multimedia (video, audio, document) analysis for law enforcement using RAG and multi-agent LLM systems (Claude 3, Legal-BERT).}
        \resumeItem{Architected and implemented multi-agent orchestration layer using MCP (Model Context Protocol) with JSON-RPC/SSE protocols, enabling agent-to-agent communication for collaborative task execution and escalation handling.}
        \resumeItem{Designed transformer fine-tuning pipelines using LoRA and QLoRA for legal domain adaptation, boosting semantic retrieval precision by 35\% while slashing inference costs by 40\%.}
        \resumeItem{Integrated Weaviate vector database with AWS SageMaker and FastAPI microservices, delivering sub-100ms hybrid search with metadata filtering and role-based access control across 100K+ document collections.}
        \resumeItem{Orchestrated asynchronous multimodal ingestion pipelines using WhisperX, OpenCV, and FFmpeg for audio-video transcription and scene understanding, accelerating processing time by 60\% and enabling Vision-Language Model capabilities.}
        \resumeItem{Established MLOps pipelines with Docker, ECS Fargate, and SageMaker for continuous model evaluation, versioning, model governance, and audit compliance in production environments.}
        \resumeItem{Mentored junior engineers on RAG architecture design, LLM prompt engineering, and vector database schema optimization; contributed to AI product roadmap and strategic integration initiatives.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Aug 2021 -- Jul 2023}
      {Airbus Group}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Enhanced aircraft 2D/3D CAD model loading performance by 75\% through microservices-based iPaaS application leveraging NestJS, Angular, AWS Application Load Balancer, and S3 optimization strategies.}
        \resumeItem{Delivered MEAN stack application that decreased CATIA license dependency by 60\%, cutting annual software costs by \$120K+ while maintaining design quality through WebSocket-based model streaming.}
        \resumeItem{Deployed OAuth-based Single Sign-On (SSO) and comprehensive API documentation using Swagger/OpenAPI; participated in Agile/Scrum and SAFe ceremonies across full SDLC.}
        \resumeItem{Automated design quality checks and optimized SQL queries from 3+ minutes to under 60 seconds, accelerating data processing for 200+ engineering workflows.}
        \resumeItem{Configured CI/CD pipelines using Jenkins on AWS ECS Docker containers with SonarQube integration for code quality gates; executed smooth MariaDB-to-MySQL migrations with zero downtime.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Data Scientist}{Aug 2019 -- Jun 2021}
      {MCR Web Solutions}{Andhra Pradesh, India}
      \resumeItemListStart
        \resumeItem{Architected optimized CNN models for image denoising, deblurring, and low-light enhancement using TensorFlow, achieving 83\% structural similarity (SSIM) improvement through hyperparameter tuning and data augmentation.}
        \resumeItem{Engineered automated ML pipeline integrating preprocessing, training, and inference with Python, TensorFlow, and AWS Lambda, cutting processing latency by 60\% and enabling on-demand image enhancement at scale.}
        \resumeItem{Deployed trained models as Docker-based microservices via RESTful APIs on AWS infrastructure for serverless execution with auto-scaling compute allocation.}
        \resumeItem{Performed exploratory data analysis (EDA) on large-scale image datasets using NumPy, Pandas, and Matplotlib to identify noise patterns and optimize feature extraction strategies.}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Engineer Intern}{May 2019 -- Jul 2019}
      {TheSmartBridge Private Limited}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Created machine learning model for chronic kidney disease diagnosis achieving 95\% accuracy using Naive Bayes, decision trees, and random forest algorithms; deployed as Django web application with user-friendly interface.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Engineering in Computer Science}{Apr 2025}
      {University of Cincinnati, College of Engineering and Applied Science}{Cincinnati, OH}
      \resumeItemListStart
        \resumeItem{GPA: 3.67/4.0}
        \resumeItem{Relevant Coursework: Machine Learning, Deep Learning, Computer Vision, Natural Language Processing, Cloud Computing, Software Engineering}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{ArthaNethra — AI Financial Risk Investigator} $|$ \emph{Python, FastAPI, Neo4j, Weaviate, Angular}}{Oct 2024 -- Nov 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Financial AI Hackathon Finalist} — Engineered knowledge graph-native financial investigation platform that automatically maps entities and relationships across multiple documents (10-Ks, contracts, invoices) into interactive graph database.}
            \resumeItem{Designed dual-database system using Neo4j for entity relationships and Weaviate for semantic vector search, enabling complex cross-document queries impossible with traditional RAG approaches.}
            \resumeItem{Constructed hybrid AI extraction pipeline combining LandingAI ADE for structured data and AWS Bedrock Claude for narrative parsing, achieving 99\% accuracy at 80\% lower cost than pure LLM approaches.}
            \resumeItem{Built explainable AI chatbot with clickable PDF citations and automatic graph generation; integrated Sigma.js for interactive visualization with multiple layout algorithms.}
            \resumeItem{Deployed full-stack application using Docker Compose; slashes M\&A due diligence time from 200+ hours to under 2 hours (90\% time reduction).}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Context-Driven Image Narration} $|$ \emph{React, Node.js, Python, TensorFlow, Transformers}}{Sep 2023 -- Feb 2024}
          \resumeItemListStart
            \resumeItem{Led development of MERN stack application with deep learning model achieving 79.7\% accuracy in object recognition using TensorFlow and Hugging Face Transformers for context-based image captioning and narration.}
            \resumeItem{Built data preprocessing pipeline for large-scale datasets and improved model performance through transfer learning with pre-trained vision-language models.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, JavaScript, TypeScript, Java, Go, SQL, C\#} \\[3pt]
     \textbf{AI/ML Technologies}{: LLMs, RAG, Knowledge Graphs, Multi-Agent Systems, LoRA/QLoRA, Prompt Engineering, PyTorch, TensorFlow, scikit-learn, Hugging Face, LangChain, LlamaIndex, Pandas, NumPy, OpenCV} \\[3pt]
     \textbf{Databases}{: Neo4j, Weaviate, Pinecone, PostgreSQL, MySQL, MongoDB, Redis, Elasticsearch} \\[3pt]
     \textbf{Cloud \& DevOps}{: AWS (SageMaker, Bedrock, Lambda, ECS Fargate, S3), Docker, Kubernetes, Jenkins, CI/CD, Git} \\[3pt]
     \textbf{Frameworks}{: FastAPI, Flask, Django, Node.js, NestJS, Angular, React, Spring Boot, ASP.NET Core} \\[3pt]
     \textbf{Development Practices}{: Agile/Scrum, Microservices, RESTful APIs, TDD, MLOps, Model Governance}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
\small{\item{
\textbf{AWS Certified Solutions Architect – Associate} \\
\textbf{Deep Learning Specialization} — DeepLearning.AI (Coursera)
}}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

